Croder: Bringing the Knowledge of the Crowds into the IDE

### 2013-05-03 paper/paper.tex
did the introduction

\newcommand{\croder}{\textsc{Croder}}
\newcommand{\ide}{\emph{IDE }}
\newcommand{\eclipse}{\emph{Eclipse }}

@@

For the scope of this paper we focused on code reviews for reasons detailed in the

what if progr tasks. integrate with IDE

specialize on code review

tool

benefit from stack exchange

preliminary used study?

@@

\section{Software development for crowds}

>>>>

\newcommand{\croder}{\textsc{Croder }}
\newcommand{\ide}{\emph{IDE }}
\newcommand{\eclipse}{\emph{Eclipse }}

@@

For the scope of this paper we choosed to focus on code reviews for reasons detailed in section~\nameref{sec:softcrowd}. In this regard we built a tool, \croder, which integrates with \eclipse to provide crowdsourced code reviews directly in the \ide.  
With \croder, programmers can build and run the whole process of code reviews directly from the \ide, from selecting code snippets, to posting the review to the crowd, to managing and accessing review outcomes.

In terms of crowd platforms we could not use Mechanical Turk because of the lack of specialized crowds. Instead, we analysed potential replacements like eLance, oDesc and Stackexchange. For reasons further in the paper we chose Stackexchange as the backend of \croder.

To evaluate the need for \croder we conducted a study to assess potential user traits and to assess programmer's knowledge of crowdsourcing and code reviews. By means of this study we were then able to build three potential user personas and intuitive UI sketches.

@@

\section{Software development for crowds}
\label{sec:softcrowd}
